Considering scale in multilayer animal social networks

### 2020-06-29 paper/manuscript.Rmd
intro edits

# Introduction
Our inference regarding the processes underlying ecological patterns
are directly linked to the scale at which they are observed [@Levin_1992;
@Allen_2015]. Animals are influenced across scales through ecological processes such as
trophic interactions, resource availability
[@Legendre_1993; @Chave_2013], and global climate and productivity [@Field_2009].
Multiscale ecology has been integrated into species distribution modelling
[@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989].
We posit that it is important to consider the scale-dependence of 
animal behaviour within the social environment to effectively understand 
complex social systems.

Social interactions exists across both temporal and spatial scales
[@Whitehead_2008]. For example, grooming requires close spatial proximity
between conspecifics and occurs over brief time periods [e.g. @Carter_2015],
whereas social associations over long time periods represent shared space use by
members of the same social group [Figure \@ref(fig:spacetime), @Franks_2009].
Individuals must share space to interact or associate and thus have overlapping
home ranges [@Vander_2014]. Home range overlap is an example of how animals
share space over coarser spatial and temporal scales [e.g. @Piza_Roca_2018].
Although the social environment clearly scales spatially and temporally, it
remains unclear whether coarser scales of social interactions, such as social
association and home range overlap, vary predictably [@Castles_2014;
@Farine_2015a]. We define social scale as the explicit definition and
measurement of social relationships [@Farine_2015a].

>>>>

# Introduction
Our inference regarding the processes underlying ecological patterns
are directly linked to the scale at which they are observed [@Levin_1992;
@Allen_2015]. Animals are influenced across scales through ecological processes such as
trophic interactions, resource availability
[@Legendre_1993; @Chave_2013], and global climate and productivity [@Field_2009].
Multiscale ecology has been integrated into species distribution modelling
[@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989].
We posit that it is important to consider the scale dependence of 
animal behaviour within the social environment to effectively understand 
complex social systems.

Social interactions exists across both temporal and spatial scales
[@Whitehead_2008]. For example, grooming requires close spatial proximity
between conspecifics and occurs over brief time periods [e.g. @Carter_2015],
whereas social associations over long time periods represent shared space use by
members of the same social group [Figure \@ref(fig:spacetime), @Franks_2009].
Individuals must share space to interact or associate and thus have overlapping
home ranges [@Vander_2014]. Home range overlap is an example of how animals
share space over coarser spatial and temporal scales [e.g. @Piza_Roca_2018].
Although the social environment scales spatially and temporally, it
remains unclear whether coarser scales of social interactions, such as social
association and home range overlap, vary predictably [@Castles_2014;
@Farine_2015a]. We define social scale as the explicit definition and
measurement of social relationships [@Farine_2015a].
